Balsa: A Compact Line Notation Based on SMILES

### 2022-07-19 manuscript.tex
Replaces stack for writing string figure with table. Closes #33

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a \textit{stack} (Figure~\ref{fig:stack}). A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack.pdf}
    \caption{Stack for branches.}
    \label{fig:stack}
\end{figure}

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a stack (Figure~\ref{fig:stack-for-writer}). A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.

% \begin{table}
%     \caption{Atomic Attributes.}
%     \centering
%     \begin{tabular}{l L l l}
%         \hline
%         Attribute & Description & Type & Default \\
%         \hline
%         \ttt{element} & Elemental symbol & \ttt{\{Element\}} & \ttt{None} \\
%         \ttt{isotope} & Mass number & \ttt{\{1..1000\}} & \ttt{None} \\
%         \ttt{hydrogens} & Hydrogen count & \ttt{Implicit}, \ttt{0..10} & 0 \\
%         \ttt{charge} & Formal charge & \ttt{-9..10} & 0 \\
%         \ttt{selected} & Selection status & \ttt{?} & \ttt{false} \\
%         \ttt{parity} & Configuration & \ttt{\{AtomParity\}} & \ttt{None} \\
%         \ttt{edges} & Edges directed toward child nodes & \ttt{[Edge]} & \ttt{[]} \\
%         \hline
%     \end{tabular}
%     \label{table:atomic-attributes}
%     \end{table}

>>>>

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a \textit{stack} (Table~\ref{table:stack-for-branches}). A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

\begin{table}
    \caption{Stack and hub for reading the string \enquote{C(N*)O}.}
    \centering
    \begin{tabular}{c c l c c}
        \hline
        Step & Character   & Action                          & Hub & Stack \\
        \hline
        1    & \enquote{C} & create atom                     & C   &       \\
        2    & \enquote{(} & push next atom                  & C   &       \\
        3    & \enquote{N} & create atom, push atom          & N   &  N    \\
        4    & \enquote{*} & create atom                     & *   &  N    \\
        5    & \enquote{)} & pop atom, update hub            & N   &       \\
        6    & \enquote{O} & create atom                     & O   &       \\
        \hline
    \end{tabular}
    \label{table:stack-for-branches}
\end{table}

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a stack (Table~\ref{table:stack-for-writing-string}). A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.
